A Domain Specific Language for SpectreGuard

### 2020-12-11 paper/main.tex
wibble

As mentioned previously, a theory of \textit{information flow} in the context of
both computer security and programming languag theory has been developed. A description
of this theory is given in~\cite{InfoFlowAnalysis}.

A significant recent work also related to the use of domain specific languages
with strong, static type systems to control information flow for security
purposes is \textit{Liquid Information Flow Control} by Polikarpova et
al.~\cite{Lifty} In this work, a novel domain specific programming language is
developed which has a static type system that is geared specifically towards
expressing security policies at a type level. As this is done within a static
type system, these invariants are machine-verified at compile-time.  Not only
can these policy violations be detected, the system they develop is also able to
fix leaks.

More broadly, a similar example of a language being represented similarly, as an
pure expression language separated from a command language, can be found in
Winskel's 1993 book in the form of the \textbf{IMP} language.\cite{WinskelBook} This
book provides an in-depth look at the three major mathematical formalizations
of programming language semantics (axiomatic semantics, operational semantics and
denotational semantics) and uses them to analyze \textbf{IMP}

>>>>

As mentioned previously, a theory of \textit{information flow} in the context of
both computer security and programming language theory has been developed. A description
of this theory is given in~\cite{InfoFlowAnalysis}.

A significant recent work also related to the use of domain specific languages
with strong, static type systems to control information flow for security
purposes is \textit{Liquid Information Flow Control} by Polikarpova et
al.~\cite{Lifty} As its title suggests, this paper also builds on the theory of information flow. In that work, a novel domain specific programming language is
developed which has a static type system that is geared specifically towards
expressing security policies at a type level. As this is done within a static
type system, these invariants are machine-verified at compile-time.  Not only
can these policy violations be detected, the system they develop is also able to
fix leaks.

More broadly, an example of a language being represented similarly, as an
pure expression language separated from a command language, can be found in
Winskel's 1993 book in the form of the \textbf{IMP} language.~\cite{WinskelBook} This
book provides an in-depth look at the three major mathematical formalizations
of programming language semantics (axiomatic semantics, operational semantics and
denotational semantics) and uses them to analyze \textbf{IMP}.
